\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-11-19 doc/flexiblesusy-paper.tex
Fixed teh way we introduce the two loop higgs corrections, sicne editd had made the start of this sentence misleading.

If higher accuracy is required, two-loop corrections to the
self-energies can be added by setting \code{UseHiggs2LoopMSSM = True}
in the MSSM or \code{UseHiggs2LoopNMSSM = True} in the NMSSM in the
model file.  The former provides routines that call the two-loop Higgs
FORTRAN routines supplied by P.~Slavich from
\cite{Degrassi:2001yf,Brignole:2001jy,Dedes:2002dy,Brignole:2002bz,Dedes:2003km}
for calculating corrections of $\oatas$, $\oabas$, $\oatq$, $\oabq$,
$\oatauq$ and $\oatab$.  The latter adds corrections calculated in the
NMSSM at $\oatas$, $\oabas$ from \cite{Degrassi:2009yq} and partial
corrections for the order $\oatq$, $\oabq$, $\oatauq$ and $\oatab$ from the
MSSM.  These corrections can then be included in the
calculation of the Higgs pole masses when running the spectrum
generator by setting the appropriate SLHA flags.

>>>>

For the Higgs states two-loop corrections to the self-energies can
optionally be added by setting \code{UseHiggs2LoopMSSM = True} in the
MSSM or \code{UseHiggs2LoopNMSSM = True} in the NMSSM in the model
file.  The former provides routines that call the two-loop Higgs
FORTRAN routines supplied by P.~Slavich from
\cite{Degrassi:2001yf,Brignole:2001jy,Dedes:2002dy,Brignole:2002bz,Dedes:2003km}
for calculating corrections of $\oatas$, $\oabas$, $\oatq$, $\oabq$,
$\oatauq$ and $\oatab$.  The latter adds corrections calculated in the
NMSSM at $\oatas$, $\oabas$ from \cite{Degrassi:2009yq} and partial
corrections for the order $\oatq$, $\oabq$, $\oatauq$ and $\oatab$
from the MSSM.  These corrections can then be included in the
calculation of the Higgs pole masses when running the spectrum
generator by setting the appropriate SLHA flags.
